Imputation of incomplete multilevel data

### 2024-02-28 manuscript.qmd

@@

>>>>

- motivation and intended audience
- the mice framework/package
- background info on missingness mechanisms etc.
- case study

# Intended audience

This tutorial aims to serve analysts who know their way around multilevel modeling, but are not (as) familiar with missing data imputation.

# Introduction

@@

# Methods

The [R]{.proglang} package [mice]{.pkg} provides a framework for imputing incomplete data on a variable-by-variable basis. The [mice]{.fct} function allows users to flexibly specify how many times and under what model the missing data should be imputed. This is reflected in the first four function arguments

```r
mice(data, m, method, predictorMatrix, ...)
```

where `data` refers to the incomplete dataset, `m` determines the number of imputations, `method` denotes the functional form of the imputation model and `predictorMatrix` specifies the interrelational dependencies between variables and imputation models (i.e., the set of predictors to be used for imputing each incomplete variable).

# References

<!-- FIMD, section 7.10 -->

<!-- > Recipe for a level-1 target:  -->
<!-- 1.	Define the most general analytic model to be applied to imputed data;  -->
<!-- 2.	Select a 2l method that imputes close to the data;  -->
<!-- 3.	Include all level-1 variables;  -->
<!-- 4.	Include the disaggregated cluster means of all level-1 variables;  -->
<!-- 5.	Include all level-1 interactions implied by the analytic model;  -->
<!-- 6.	Include all level-2 predictors;  -->
<!-- 7.	Include all level-2 interactions implied by the analytic model;  -->
<!-- 8.	Include all cross-level interactions implied by the analytic model;  -->
<!-- 9.	Include predictors related to the missingness and the target;  -->
<!-- 10.	Exclude any terms involving the target -->

<!-- > Recipe for a level-2 target:  -->
<!-- 1.	Define the most general analytic model to be applied to imputed -->
<!-- data;  -->
<!-- 2.	Select a 2lonly method that imputes close to the data;  -->
<!-- 3.	Include the cluster means of all level-1 variables;  -->
<!-- 4.	Include the cluster means of all level-1 interactions;  -->
<!-- 5.	Include all level-2 predictors;  -->
<!-- 6.	Include all interactions of level-2 variables;  -->
<!-- 7.	Include predictors related to the missingness and the target;  -->
<!-- 8.	Exclude any terms involving the target -->
